Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-06 paper.tex
Add regression table.

% Document-specific definitions
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}

@@

OLS, controls

\subsection{Empirical Results}

>>>>

% Document-specific definitions
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\+}{\phantom{-}}

@@

We model performance and efficiency in WikiProjects using ordinary least-squares linear regression.
Each WikiProject is taken as a single observation.
The models include each project's coeditor network properties as independent variables.
We also include several project-level variables to control for confounding factors.
Some variables are log-transformed to reduce heteroscedasticity.

Our models are summarized in Table \ref{tab:model}.
Mean min-cut was found to be highly correlated with degree (see Figure \ref{fig:degree-mincut}),
so we exclude min-cut to prevent collinearity.
The high correlation between mean degree and min-cut implies that in most cases
the minimum $st$-cut is simply the either set of edges from $s$ or the set of edges to $t$.
The rarity of non-trivial min-cuts suggests that WikiProject coeditor networks have very few central
bottlenecks and are thus highly decentralized.

\begin{figure}
\caption{
TODO
\label{fig:degree-mincut}
}
\end{figure}

\begin{table*}
\begin{tabular}{llc}
 & Performance$^\dagger$ & Performance$^\dagger$ \\
\hline
Mean Degree$^\dagger$          &  -0.8$^{***}$  & \\
In-Degree Skewness$^\dagger$   &  -0.6$^{***}$  & \\
Out-Degree Skewness$^\dagger$  &               & \\
Mean Path$^\dagger$            &  -0.36$^{***}$ & \\
C-Eff$^\dagger$                &  -0.08$^{**}$  & \\
Connectivity                   & \+0.02         & \\
Mean Editors/Article$^\dagger$ & \+0.4$^{***}$  & \\
Article Count$^\dagger$        &  -0.3          & \\
Editor Count$^\dagger$         & \+0.7$^{*}$    & \\
Revision Count$^\dagger$       & \+0.4          & \\
First Assessment               & \+0.03         & \\
Mean Article Age               &  -0.04         & \\
\hline
DoF                            & 1278           & \\
R$^2$(adj)                       & 0.37           & \\
\end{tabular}
\caption{
\label{tab:model}
}
\end{table*}
